---
title: 'Strand Specific Effect Size Extraction.Rmd'
author: "Jonathan Reardon"
output:
  html_document:
    keep_md: true
    df_print: paged
  #pdf_document:
    #keep_md: true
editor_options:
  chunk_output_type: inline
---

```{r setup, message=FALSE}
knitr::opts_chunk$set(echo = T,
                      fig.path = "StrandSpecificEffectSizeExtraction_figs/")
library(reticulate)
library(ggplot2)
library(dplyr)
library(reshape2)
use_python("/usr/local/bin/python3")
```

**Get data with Python**
```{python}
import json
from collections import Counter
from pprint import pprint
from matplotlib import pyplot as plt
import pandas as pd
plt.style.use('ggplot')

# import dataset
with open('/home/jon/json/Batch1.json') as f:
    data=json.load(f)
    
###################################################
### GET STRAND LABELS AND KEYS FROM TOP OUTER LAYER
###################################################

def get_strand_info():
    ''' 
    a function that returns
    a dict containing strand labels
    and corresponding attribute ids
    '''
    strands={}
    for counter, element in enumerate(data["CodeSets"][0]["Attributes"]["AttributesList"]):
        attribute_name=(data["CodeSets"][0]["Attributes"]["AttributesList"][counter]["AttributeName"])
        attribute_id=(data["CodeSets"][0]["Attributes"]["AttributesList"][counter]["AttributeId"])
        strands.update( {attribute_id:attribute_name} )
    return strands
    
######################################
### DISPLAY STRAND SUMMARY INFORMATION 
######################################
    
def get_strand_summary():
    '''
    A function that produces a basic
    summary of strand study counts
    and a graph to display them
    '''
    global counts, strand_title
    strand_overview=[]
    for element in range(len(data["References"])):
        for key, value in strands.items():
            for section in range(len(data["References"][element]["Codes"])):
                if key == data["References"][element]["Codes"][section]["AttributeId"]:
                    a=(data["References"][element]["ItemId"])
                    b=(data["References"][element]["Title"])
                    strand_overview.append([value, key, a, b])

    strand_title=[]
    for element in strand_overview:
        strand_title.append(element[0])

    counts = Counter(strand_title) 
    pprint(counts)

#######################################
### GET THE ID FOR OUR STRAND OF CHOICE 
#######################################

def get_strand_value(strand_label):
    ''' 
    A function that takes in a 
    strand name and returns
    the strand ID
    '''
    for key, value in strands.items():
        if value == strand_label:
            return key, value

######################################################
###  GET EFFECT SIZE INFO FROM STRAND SPECIFIC STUDIES
######################################################

def get_data(strand_key, strand_value, outcome_choice):
    '''
    A function that accepts a strand id and a variable of
    interest and returns a list of that id and the variable
    values.
    '''
    outcome_studies=[] 

    # iterate over each section of 'references'
    for section in range(len(data["References"])):
        # iterate over each study within each section of 'references'
        for study in range(len(data["References"][section]["Codes"])):
            # check each study to see if strand id is present
            if strand_id[0] == data["References"][section]["Codes"][study]["AttributeId"]:
                if "Outcomes" in data["References"][section]:
                    if data["References"][section]["Outcomes"][0]["OutcomeText"] == outcome_choice:
                        outcome_id=((data["References"][section]["Outcomes"][0]["OutcomeId"]))
                        outcome_type=(data["References"][section]["Outcomes"][0]["ShortTitle"])
                        outcome_text=(data["References"][section]["Outcomes"][0]["OutcomeText"])
                        SMD=(data["References"][section]["Outcomes"][0]["SMD"])
                        SESMD=(data["References"][section]["Outcomes"][0]["SESMD"])
                        CIupperSMD=(data["References"][section]["Outcomes"][0]["CIUpperSMD"])
                        CIlowerSMD=(data["References"][section]["Outcomes"][0]["CILowerSMD"])
                        year=(data["References"][section]["Year"])
                        intervention=(data["References"][section]["Outcomes"][0]["InterventionText"])
                        outcome_studies.append([strand_key, strand_value, outcome_id, outcome_text, 
                                                outcome_type, year, intervention, SMD, SESMD, CIupperSMD,
                                                CIlowerSMD])
              
    # display number of studies found within selected strand
    print('Number of studies within strand {}: {}'.format(strand_value, len(outcome_studies)), "\n")
    
    pd.set_option('display.max_rows', 15)
    pd.set_option('display.max_columns', 15)
    
    # convert data list to pandas dataframe for viewing
    df_primary = pd.DataFrame(outcome_studies, columns=['AttributeId', 'Strand', 'OutcomeId', 'OutcomeType', 
                                                        'ShortTitle', 'Year', 'Intervention', 'SMD', 'SESMD',
                                                        'CIupper', 'CIlower'])
    
    # round effect sizes to two decimal points
    df_primary.loc[:, "SMD"] = df_primary["SMD"].astype(float).round(4)
    df_primary.loc[:, "SESMD"] = df_primary["SESMD"].astype(float).round(4)
    df_primary.loc[:, "CIupper"] = df_primary["CIupper"].astype(float).round(4)
    df_primary.loc[:, "CIlower"] = df_primary["CIlower"].astype(float).round(4)
    
    return df_primary

strands = get_strand_info()
get_strand_summary()
```
```{python}
strand_id = get_strand_value("Oral language interventions") 
oral_lang = get_data(strand_id[0], strand_id[1], "Primary outcome")

oral_lang.head(10)
```
Pass 'oral language' strand pandas dataframe to R (as R dataframe) and make forest plot
```{r, message=FALSE, fig.width=8,fig.height=12}
oral_lang_df <- data.frame(py$oral_lang) # convert pandas dataframe (python) to R dataframe

ggplot(oral_lang_df, aes(y=ShortTitle, x=SMD, xmin=CIlower, xmax=CIupper))+
  geom_point(color='black', shape=15) +
  geom_errorbarh(height=.7, linetype=1) +
  scale_x_continuous(limits=c(-3,3), name='Standardized Mean Difference (95% CI)') +
  ylab('Reference') +
  geom_vline(xintercept=0, color='black', linetype='dashed') +
  theme_classic()
```
```{r, fig.width=11,fig.height=5}
# prepare data for dotplot
oral_lang_df$Intervention <- as.character(oral_lang_df$Intervention)
oral_lang_df$Intervention[oral_lang_df$Intervention==""] <- NA
oral_lang_df$Intervention <- as.factor(oral_lang_df$Intervention)
oral_lang_mean_SMD <- mean(oral_lang_df$SMD, na.rm=TRUE)
oral_lang_mean_SESMD <- mean(oral_lang_df$SESMD, na.rm=TRUE)

# View(oral_lang_df) # uncomment to view data in data viewer

ggplot(data=subset(oral_lang_df, !is.na(Intervention)), aes(SMD, SESMD, color=Intervention)) + 
    geom_point(alpha=1, na.rm=TRUE, size=3) +
    theme_grey() +
    geom_vline(xintercept=oral_lang_mean_SMD, linetype="dotted", color="black", size=1) +
    theme(legend.title = element_text(color = "black", size = 10),
          legend.text = element_text(color = "black", size = 8)) +
    theme(legend.position="right") +
    guides(fill=guide_legend(nrow=5, byrow=TRUE)) +
    theme(legend.title=element_blank()) +
    annotate(geom="text", x=oral_lang_mean_SMD+.15, y=-.1, label=round(oral_lang_mean_SMD, 2), color="black") +
    ylim(-0.2, 1.75) +
    ggtitle("SMD by SESMD broken down by Intervention, Oral Language strand, Primary outcome")
```

Get 'Feedback' strand data (effect sizes and confidence intervals) for Primary outcome studies
```{python}
strand_id = get_strand_value("Feedback") 
feedback = get_data(strand_id[0], strand_id[1], "Primary outcome")

feedback.head(10)
```
Pass 'feedback' strand pandas dataframe to R (as R dataframe) and make forest plot
```{r, message=FALSE, fig.width=8,fig.height=12}
feedback_df <- data.frame(py$feedback) # convert pandas dataframe (python) to R dataframe

ggplot(feedback_df, aes(y=ShortTitle, x=SMD, xmin=CIlower, xmax=CIupper))+
  geom_point(color='black', shape=15) +
  geom_errorbarh(height=.7, linetype=1) +
  scale_x_continuous(limits=c(-3,3), name='Standardized Mean Difference (95% CI)') +
  ylab('Reference') +
  geom_vline(xintercept=0, color='black', linetype='dashed') +
  theme_classic()
```

```{r, fig.width=11,fig.height=5}
# prepare data for dotplot
feedback_df$Intervention <- as.character(feedback_df$Intervention)
feedback_df$Intervention[feedback_df$Intervention==""] <- NA
feedback_df$Intervention <- as.factor(feedback_df$Intervention)
feedback_mean_SMD <- mean(feedback_df$SMD, na.rm=TRUE)
feedback_mean_SESMD <- mean(feedback_df$SESMD, na.rm=TRUE)

# View(feedback_df) # uncomment to view data in dataviewer

ggplot(data=subset(feedback_df, !is.na(Intervention)), aes(SMD, SESMD, color=Intervention)) + 
    geom_point(alpha=1, na.rm=TRUE, size=3) +
    theme_grey() +
    geom_vline(xintercept=feedback_mean_SMD, linetype="dotted", color="black", size=1) +
    theme(legend.title = element_text(color = "black", size = 10),
          legend.text = element_text(color = "black", size = 8)) +
    theme(legend.position="right") +
    guides(fill=guide_legend(nrow=5, byrow=TRUE)) +
    theme(legend.title=element_blank()) +
    annotate(geom="text", x=feedback_mean_SMD+.15, y=-.1, label=round(feedback_mean_SMD, 2), color="black") +
    ylim(-0.2, 1.75) +
    ggtitle("SMD by SESMD broken down by Intervention, Feedback strand only")
```

Get 'Peer tutoring' strand data (effect sizes and confidence intervals) for Primary outcome studies
```{python}
strand_id = get_strand_value("Peer tutoring") 
peertutor = get_data(strand_id[0], strand_id[1], "Primary outcome")

peertutor.head(10)
```
Pass 'peer tutoring' strand pandas dataframe to R (as R dataframe) and make forest plot
```{r, message=FALSE, fig.width=8,fig.height=12}
peer_tutoring_df <- data.frame(py$peertutor) # convert pandas dataframe (python) to R dataframe

ggplot(feedback_df, aes(y=ShortTitle, x=SMD, xmin=CIlower, xmax=CIupper))+
  geom_point(color='black', shape=15) +
  geom_errorbarh(height=.7, linetype=1) +
  scale_x_continuous(limits=c(-3,3), name='Standardized Mean Difference (95% CI)') +
  ylab('Reference') +
  geom_vline(xintercept=0, color='black', linetype='dashed') +
  theme_classic()
```
```{r, fig.width=11,fig.height=5}
# prepare data for dotplot
peer_tutoring_df$Intervention <- as.character(peer_tutoring_df$Intervention)
peer_tutoring_df$Intervention[feedback_df$Intervention==""] <- NA
peer_tutoring_df$Intervention <- as.factor(peer_tutoring_df$Intervention)
peer_tutoring_df_SMD <- mean(peer_tutoring_df$SMD, na.rm=TRUE)
peer_tutoring_df_SESMD <- mean(peer_tutoring_df$SESMD, na.rm=TRUE)

# View(feedback_df) # uncomment to view data in dataviewer

ggplot(data=subset(peer_tutoring_df, !is.na(Intervention)), aes(SMD, SESMD, color=Intervention)) + 
    geom_point(alpha=1, na.rm=TRUE, size=3) +
    theme_grey() +
    geom_vline(xintercept=peer_tutoring_df_SMD, linetype="dotted", color="black", size=1) +
    theme(legend.title = element_text(color = "black", size = 10),
          legend.text = element_text(color = "black", size = 8)) +
    theme(legend.position="right") +
    guides(fill=guide_legend(nrow=5, byrow=TRUE)) +
    theme(legend.title=element_blank()) +
    annotate(geom="text", x=peer_tutoring_df_SMD+.15, y=-.1, label=round(peer_tutoring_df_SMD, 2), color="black") +
    ylim(-0.2, 1.75) +
    ggtitle("SMD by SESMD broken down by Intervention, Peer tutoring strand only")
```

```{python}
strand_id = get_strand_value("Teaching assistants") 
teachingassist = get_data(strand_id[0], strand_id[1], "Primary outcome")

teachingassist.head(10)
```
Pass 'teaching assistants' strand pandas dataframe to R (as R dataframe) and make forest plot
```{r, message=FALSE, fig.width=8,fig.height=8}
teaching_assistants_df <- data.frame(py$teachingassist)

ggplot(teaching_assistants_df, aes(y=ShortTitle, x=SMD, xmin=CIlower, xmax=CIupper))+
  geom_point(color='black', shape=15) +
  geom_errorbarh(height=.4, linetype=1) +
  scale_x_continuous(limits=c(-3,3), name='Standardized Mean Difference (95% CI)') +
  ylab('Reference') +
  geom_vline(xintercept=0, color='black', linetype='dashed') +
  theme_classic()
```
```{r, fig.width=11,fig.height=5}
# prepare data for dotplot
teaching_assistants_df$Intervention <- as.character(teaching_assistants_df$Intervention)
teaching_assistants_df$Intervention[teaching_assistants_df$Intervention==""] <- NA
teaching_assistants_df$Intervention <- as.factor(teaching_assistants_df$Intervention)
teaching_assistants_df_SMD <- mean(teaching_assistants_df$SMD, na.rm=TRUE)
teaching_assistants_df_SESMD <- mean(teaching_assistants_df$SESMD, na.rm=TRUE)

# View(feedback_df) # uncomment to view data in dataviewer

ggplot(data=subset(teaching_assistants_df, !is.na(Intervention)), aes(SMD, SESMD, color=Intervention)) + 
    geom_point(alpha=1, na.rm=TRUE, size=3) +
    theme_grey() +
    geom_vline(xintercept=teaching_assistants_df_SMD, linetype="dotted", color="black", size=1) +
    theme(legend.title = element_text(color = "black", size = 10),
          legend.text = element_text(color = "black", size = 8)) +
    theme(legend.position="right") +
    guides(fill=guide_legend(nrow=5, byrow=TRUE)) +
    theme(legend.title=element_blank()) +
    annotate(geom="text", x=peer_tutoring_df_SMD+.15, y=-.1, label=round(teaching_assistants_df_SMD, 2), color="black") +
    ylim(-0.2, 1.75) +
    ggtitle("SMD by SESMD broken down by Intervention, Teaching assistants strand only")
```

Call 'get data' function several times (for different strands) and combine into one 'master' dataframe
```{python}
strand_id = get_strand_value("Oral language interventions") 
oral_lang = get_data(strand_id[0], strand_id[1], "Primary outcome")

strand_id = get_strand_value("Feedback") 
feedback = get_data(strand_id[0], strand_id[1], "Primary outcome")

strand_id = get_strand_value("Peer tutoring") 
peer_tut = get_data(strand_id[0], strand_id[1], "Primary outcome")

strand_id = get_strand_value("Teaching assistants") 
teaching_assist = get_data(strand_id[0], strand_id[1], "Primary outcome")

strand_id = get_strand_value("Small group tuition") 
small_group = get_data(strand_id[0], strand_id[1], "Primary outcome")

strand_id = get_strand_value("One to one tuition") 
one_to_one = get_data(strand_id[0], strand_id[1], "Primary outcome")

master_df = pd.concat([oral_lang, feedback, peer_tut, teaching_assist, small_group, one_to_one])
master_df
```
Pass the 'master' dataframe from Python to R
```{r, fig.width=12,fig.height=5}
master_df <- data.frame(py$master_df)
master_df$Intervention[master_df$Intervention==""] <- NA

View(master_df)
           
filter(master_df, !is.na(Intervention)) %>%
  ggplot(aes(fill=Intervention, y=SMD, x=Strand)) +
  geom_bar(position="dodge", stat="identity", color="black", na.rm=TRUE) +
  ggtitle("SMD by Strand, broken down by Intervention")
```

```{r, fig.width=12,fig.height=5}
filter(master_df, !is.na(Intervention)) %>%
  ggplot(aes(y=SMD, x=Strand, size=Intervention, color=Intervention)) +
  geom_jitter(shape=16, position=position_jitter(.2), size=2, shape=21)
```

```{r, fig.width=12,fig.height=5}
filter(master_df, !is.na(Intervention)) %>%
  ggplot(aes(fill=Intervention, y=SMD, x=Strand)) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=.6, binwidth=.2, na.rm=TRUE) +
  ggtitle("SMD by Strand, broken down by Intervention")
```

