---
title: 'Summary_Info.Rmd'
author: "Jonathan Reardon"
output:
  html_document:
    keep_md: true
    #df_print: paged
  #pdf_document:
    #keep_md: true
editor_options:
  chunk_output_type: inline
---

**Import R libraries, save figures to "Master_figs/"**
```{r setup, message=FALSE}
knitr::opts_chunk$set(echo = T,
                      fig.path = "Master_figs/")
library(reticulate)
library(ggplot2)
library(dplyr)
library(reshape2)
library(purrr)
library(gridExtra)
library(cowplot)
library(kableExtra)
library(forestplot)
library(metafor)
use_python("/usr/local/bin/python3")
rm(list = ls())
```
**Import Python packages and (json) dataset**
```{python}
# import necessary libraries
import json
from collections import Counter
from pprint import pprint
import numpy as np
from matplotlib import pyplot as plt
import pandas as pd
plt.style.use('ggplot')

# import dataset (uncomment to select dataset of choice)
#with open('/home/jon/json/ToolkitExtraction/data/batch2.json') as f:
#with open('/home/jon/json/ToolkitExtraction/data/Batch1.json') as f:
#with open('/home/jon/json/ToolkitExtraction/data/May11th_2020.json') as f:
with open('/home/jon/json/ToolkitExtraction/data/May 12th_2020.json') as f:
    data=json.load(f)
```
**Flatten dataset into lists containing all attribute names and Ids to easily get top-level (CodeSets) information**
```{python}
def extract_values(obj, key):
    """Pull all values of specified key from nested JSON."""
    arr = []
    def extract(obj, arr, key):
        """Recursively search for values of key in JSON tree."""
        if isinstance(obj, dict):
            for k, v in obj.items():
                if isinstance(v, (dict, list)):
                    extract(v, arr, key)
                elif k == key:
                    arr.append(v)
        elif isinstance(obj, list):
            for item in obj:
                extract(item, arr, key)
        return arr

    results = extract(obj, arr, key)
    return results

x = extract_values(data,'AttributeName')
y = extract_values(data,'AttributeId')

df=[]
for xs, ys in zip(x, y):
    df.append([xs, ys])
```
## CodeSets extraction

These functions extract attribute names and ID's (e.g. strand, educational setting) and return Python dictionaries containing attribute ID's as 'keys' and attribute names as 'values'. The 'Codesets' section at the top of the file does not contain any data, only variable information.

**Example dictionaries**  
strands&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;= {5023544: 'Arts participation', 5023545: 'Aspiration interventions', .. }  
edu_setting&nbsp;&nbsp;&nbsp;= {5215410: 'Nursery school/pre-school', 5215411: 'Primary/elementary school', 5215412, .. }

```{python}
### CONSTANTS ###
exclude="NA"
# Variable counts
strand_options=34
design_options=10
edu_setting_options=12
country_options=188
pub_Type_options=6
age_options=18
gender_options=5
realism_options=4
participant_assignment_options=8

# LEVEL OF ASSIGNMENT
def get_level_of_assignment_info():
    level_of_assignment={}
    for counter, item in enumerate(df):
        if item[0] == "What was the level of assignment?":
            for i in range(1,7):
                level_of_assignment.update( {df[counter+i][1]:df[counter+i][0]} ) 
    return level_of_assignment
level_of_assignment = get_level_of_assignment_info()

# PARTICIPANT ASSIGNMENT
def get_participant_assignment_info():
    participant_assignment={}
    for counter, item in enumerate(df):
        if item[0] == "How were participants assigned?":
            for i in range(1,participant_assignment_options):
                participant_assignment.update( {df[counter+i][1]:df[counter+i][0]} )
    return participant_assignment
participant_assignment = get_participant_assignment_info()

# STUDY REALISM
def get_study_realism_info():
    study_realism={}
    for counter, item in enumerate(df):
        if item[0] == "How realistic was the study?":
            for i in range(1,realism_options):
                study_realism.update( {df[counter+i][1]:df[counter+i][0]} ) 
    return study_realism
study_realism = get_study_realism_info()

# STUDENT GENDER
def get_student_gender_info():
    student_gender={}
    for counter, item in enumerate(df):
        if item[0] == "What is the gender of the students?":
            for i in range(1,gender_options):
                student_gender.update( {df[counter+i][1]:df[counter+i][0]} ) 
    return student_gender
student_gender = get_student_gender_info()

# STUDENT AGE
def get_student_age_info():
    student_age={}
    for counter, item in enumerate(df):
        if item[0] == "What is the age of the students? (Select ALL that apply)":
            for i in range(1,age_options):
                student_age.update( {df[counter+i][1]:df[counter+i][0]} ) 
    return student_age
student_age = get_student_age_info()

# PUBLICATION TYPE
def get_pub_type_info():
    pub_type={}
    for counter, item in enumerate(df):
        if item[0] == "Section 1 What is the publication type?":
            for i in range(1,pub_Type_options):
                pub_type.update( {df[counter+i][1]:df[counter+i][0]} )
    return pub_type
pub_type = get_pub_type_info()

# STRAND
def get_strand_info():
    strands={}
    for counter, item in enumerate(df):
        if item[0] == "Toolkit strand(s) (select at least one Toolkit strand)":
            for i in range(1,strand_options):
                strands.update( {df[counter+i][1]:df[counter+i][0]} )
    return strands
strand_codes = get_strand_info()

# STUDY DESIGN
def get_study_design_info():
    study_design={}
    for counter, item in enumerate(df):
        if item[0] == "What was the study design?":
            for i in range(1,design_options):
                study_design.update( {df[counter+i][1]:df[counter+i][0]} )
    return study_design
study_design = get_study_design_info()

# EDUCATIONAL SETTING
def get_edu_setting_info():
    edu_setting={}
    for counter, item in enumerate(df):
        if item[0] == "What is the educational setting (Select ALL that apply)":
            for i in range(1,edu_setting_options):
                edu_setting.update( {df[counter+i][1]:df[counter+i][0]} )   
    return edu_setting
edu_setting = get_edu_setting_info()

# COUNTRIES
def get_countries_info():
    countries={}
    for counter, item in enumerate(df):
        if item[0] == "In which country/countries was the study carried out? (Select ALL that apply)":
            for i in range(1,country_options):
                countries.update( {df[counter+i][1]:df[counter+i][0]} ) 
    return countries
countries = get_countries_info()
```

```{python}
def get_strands():
  finds=[]
    
  for section in range(len(data["References"])):
      if "Codes" in data["References"][section]:
          if "Outcomes" in data["References"][section]:
              if "OutcomeCodes" in data["References"][section]["Outcomes"][0]:
                  for study in range(len(data["References"][section]["Outcomes"][0]["OutcomeCodes"]["OutcomeItemAttributesList"])):
                      for key,value in strand_codes.items():
                          if key == data["References"][section]["Outcomes"][0]["OutcomeCodes"]["OutcomeItemAttributesList"][study]["AttributeId"]:
                              strandfind=value
                  finds.append(strandfind)
              else:
                  finds.append(exclude)
          else:
              finds.append(exclude)
      else:
          finds.append(exclude)
        
  return finds

strand_info = get_strands() 

#lst=[]
#for k,v in strand_codes.items():
    #lst.append(v)
    #for obj in lst:
        #if strand_info.count(obj) > 0:
            #print(obj, strand_info.count(obj))
         
  #count_summary()
```

```{python}
levelofassignment=[]

assigncomment=[]
for section in range(len(data["References"])):
    if "Codes" in data["References"][section]:
        levelassignfind, levelassignvalue = exclude, exclude
        perstudy=[]
        for study in range(len(data["References"][section]["Codes"])):
            for key,value in level_of_assignment.items():
                if key == data["References"][section]["Codes"][study]["AttributeId"]:
                    levelassignfind, levelassignvalue = value, key
                    perstudy.append(data["References"][section]["Codes"][study]["AdditionalText"])
                    if "ItemAttributeFullTextDetails" in data["References"][section]["Codes"][study]:
                        for i in range(len(data["References"][section]["Codes"][study]["ItemAttributeFullTextDetails"])):
                             perstudy.append(data["References"][section]["Codes"][study]["ItemAttributeFullTextDetails"][i]["Text"])
        assigncomment.append(perstudy)
        levelofassignment.append([levelassignfind])
    else:
        levelofassignment.append([exclude])
        
```

```{python}
design=[]
designcomment=[]
for section in range(len(data["References"])):
    if "Codes" in data["References"][section]:
        designfind, designlabel= exclude, exclude
        perstudy=[]
        for study in range(len(data["References"][section]["Codes"])):
            for key, value in study_design.items():
                if key == data["References"][section]["Codes"][study]["AttributeId"]:
                    designfind, designlabel = value, key
                    perstudy.append(data["References"][section]["Codes"][study]["AdditionalText"])
                    if "ItemAttributeFullTextDetails" in data["References"][section]["Codes"][study]:
                        for i in range(len(data["References"][section]["Codes"][study]["ItemAttributeFullTextDetails"])):
                            perstudy.append(data["References"][section]["Codes"][study]["ItemAttributeFullTextDetails"][i]["Text"])
        designcomment.append(perstudy)
        design.append(designfind)
    else:
        design.append(exclude)
```

```{python}
studyrealism=[]
studyrealismcomment=[]
for section in range(len(data["References"])):
    if "Codes" in data["References"][section]:
        realismfind, realismvalue = exclude, exclude
        perstudy=[]
        for study in range(len(data["References"][section]["Codes"])):
            for key,value in study_realism.items():
                if key == data["References"][section]["Codes"][study]["AttributeId"]:
                    realismfind, realismvalue = value, key
                    perstudy.append(data["References"][section]["Codes"][study]["AdditionalText"])
                    if "ItemAttributeFullTextDetails" in data["References"][section]["Codes"][study]:
                        for i in range(len(data["References"][section]["Codes"][study]["ItemAttributeFullTextDetails"])):
                            perstudy.append(data["References"][section]["Codes"][study]["ItemAttributeFullTextDetails"][i]["Text"])
        studyrealismcomment.append(perstudy)
        studyrealism.append(realismfind)
    else:
        studyrealism.append([exclude])

```

```{python}
studentgender=[]
studentgendercomments=[]
for section in range(len(data["References"])):
    if "Codes" in data["References"][section]:
        genderfind, gendervalue = exclude, exclude
        perstudy=[]
        for study in range(len(data["References"][section]["Codes"])):
            for key,value in student_gender.items():
                if key == data["References"][section]["Codes"][study]["AttributeId"]:
                    genderfind, gendervalue = value, key
                    perstudy.append(data["References"][section]["Codes"][study]["AdditionalText"])
                    if "ItemAttributeFullTextDetails" in data["References"][section]["Codes"][study]:
                        for i in range(len(data["References"][section]["Codes"][study]["ItemAttributeFullTextDetails"])):
                            perstudy.append(data["References"][section]["Codes"][study]["ItemAttributeFullTextDetails"][i]["Text"])
        studentgendercomments.append(perstudy)
        studentgender.append([genderfind])
    else:
        studentgender.append([exclude])

```

```{python}

age=[]
agecomments=[]
for section in range(len(data["References"])):
    find=0
    if "Codes" in data["References"][section]:
        studentagefind, studentagelabel = [], []
        perstudy=[]
        for study in range(len(data["References"][section]["Codes"])):
            for key, value in student_age.items():
                if key == data["References"][section]["Codes"][study]["AttributeId"]:
                    studentagefind.append(value)
                    studentagelabel.append(key)
                    if data["References"][section]["Codes"][study]["AdditionalText"]:
                        perstudy.append(data["References"][section]["Codes"][study]["AdditionalText"])
                    if "ItemAttributeFullTextDetails" in data["References"][section]["Codes"][study]:
                        if data["References"][section]["Codes"][study]["ItemAttributeFullTextDetails"]:
                            for i in range(len(data["References"][section]["Codes"][study]["ItemAttributeFullTextDetails"])):
                                perstudy.append(data["References"][section]["Codes"][study]["ItemAttributeFullTextDetails"][i]["Text"])
                elif find==0:
                    pass
        if len(perstudy) ==0:
            perstudy="NA"
        agecomments.append(perstudy)
        age.append(studentagefind)


pprint(agecomments)
```

```{python}

pub=[]
pubcomments=[]
for section in range(len(data["References"])):
    if "Codes" in data["References"][section]:
        pubfind, publabel= exclude, exclude
        perstudy=[]
        for study in range(len(data["References"][section]["Codes"])):
            for key, value in pub_type.items():
                if key == data["References"][section]["Codes"][study]["AttributeId"]:
                    pubfind, publabel = value, key
                    perstudy.append(data["References"][section]["Codes"][study]["AdditionalText"])
                    if "ItemAttributeFullTextDetails" in data["References"][section]["Codes"][study]:
                        for i in range(len(data["References"][section]["Codes"][study]["ItemAttributeFullTextDetails"])):
                            perstudy.append(data["References"][section]["Codes"][study]["ItemAttributeFullTextDetails"][i]["Text"])
        pubcomments.append(perstudy)
        pub.append(pubfind)
    else:
        pub.append(exclude)
```

```{python}

partassignment=[]
partassigncomments=[]
for section in range(len(data["References"])):
    if "Codes" in data["References"][section]:
        partassignfind, partassignvalue = exclude, exclude
        perstudy=[]
        for study in range(len(data["References"][section]["Codes"])):
            for key,value in participant_assignment.items():
                if key == data["References"][section]["Codes"][study]["AttributeId"]:
                    partassignfind, partassignvalue = value, key
                    perstudy.append(data["References"][section]["Codes"][study]["AdditionalText"])
                    if "ItemAttributeFullTextDetails" in data["References"][section]["Codes"][study]:
                        for i in range(len(data["References"][section]["Codes"][study]["ItemAttributeFullTextDetails"])):
                            perstudy.append(data["References"][section]["Codes"][study]["ItemAttributeFullTextDetails"][i]["Text"])
        partassigncomments.append(perstudy)
        partassignment.append([partassignfind])
    else:
        partassignment.append([exclude])

```

```{python}

edusetting=[]
edusettingcomments=[]
for section in range(len(data["References"])):
    if "Codes" in data["References"][section]:
        edusettingfind, edusettingvalue = exclude, exclude
        perstudy=[]
        for study in range(len(data["References"][section]["Codes"])):
            for key,value in edu_setting.items():
                if key == data["References"][section]["Codes"][study]["AttributeId"]:
                    edusettingfind, edusettingvalue = value, key
                    perstudy.append(data["References"][section]["Codes"][study]["AdditionalText"])
                    if "ItemAttributeFullTextDetails" in data["References"][section]["Codes"][study]:
                        for i in range(len(data["References"][section]["Codes"][study]["ItemAttributeFullTextDetails"])):
                            perstudy.append(data["References"][section]["Codes"][study]["ItemAttributeFullTextDetails"][i]["Text"])
        edusettingcomments.append(perstudy)
        edusetting.append([edusettingfind])
    else:
        edusetting.append([exclude])

```

```{python}

country=[]
countrycomments=[]
for section in range(len(data["References"])):
    if "Codes" in data["References"][section]:
        countryfind, countryvalue = exclude, exclude
        perstudy=[]
        for study in range(len(data["References"][section]["Codes"])):
            for key,value in countries.items():
                if key == data["References"][section]["Codes"][study]["AttributeId"]:
                    countryfind, countryvalue = value, key
                    perstudy.append(data["References"][section]["Codes"][study]["AdditionalText"])
                    if "ItemAttributeFullTextDetails" in data["References"][section]["Codes"][study]:
                        for i in range(len(data["References"][section]["Codes"][study]["ItemAttributeFullTextDetails"])):
                            perstudy.append(data["References"][section]["Codes"][study]["ItemAttributeFullTextDetails"][i]["Text"])
        countrycomments.append(perstudy)
        country.append([countryfind])
    else:
        country.append([exclude])

```

```{python}
titles=[]
for section in range(len(data["References"])):
    if "ShortTitle" in data["References"][section]:
        titles.append(data["References"][section]["ShortTitle"])
```

```{python}
year=[]
for section in range(len(data["References"])):
    if "Year" in data["References"][section]:
        year.append(int(data["References"][section]["Year"]))
    else:
        year.append(exclude)
```
```{python}

codes_check=[]
outcomes_check=[]
outcomecodes_check=[]

for section in range(len(data["References"])):
    Codes="No"
    Outcomes="No"
    OutcomeCodes="No"
    if "Codes" in data["References"][section]:
        Codes="Yes"
        if "Outcomes" in data["References"][section]:
            Outcomes="Yes"
            if "OutcomeCodes" in data["References"][section]["Outcomes"][0]:
                OutcomeCodes="Yes"
          
    codes_check.append(Codes)
    outcomes_check.append(Outcomes)
    outcomecodes_check.append(OutcomeCodes)
```

```{python}
itemids=[]
for section in range(len(data["References"])):
  if "ItemId" in  data["References"][section]:
      itemids.append(data["References"][section]["ItemId"])
  else:
      itemid=exclude
```
```{python}
outcometext=[]
interventiontext=[]
SMD=[]
SESMD=[]
CIupperSMD=[]
CIlowerSMD=[]

for section in range(len(data["References"])):
    if "Outcomes" in data["References"][section]:
        outcometext.append(data["References"][section]["Outcomes"][0]["OutcomeText"])
        interventiontext.append(data["References"][section]["Outcomes"][0]["InterventionText"])
        SMD.append(data["References"][section]["Outcomes"][0]["SMD"])
        SESMD.append(data["References"][section]["Outcomes"][0]["SESMD"])
        CIupperSMD.append(data["References"][section]["Outcomes"][0]["CIUpperSMD"])
        CIlowerSMD.append(data["References"][section]["Outcomes"][0]["CILowerSMD"])
                  
    else:
        outcometext.append(exclude)
        interventiontext.append(exclude)
        SMD.append(exclude)
        SESMD.append(exclude)
        CIupperSMD.append(exclude)
        CIlowerSMD.append(exclude)
```

```{python}

df = pd.DataFrame(list(zip(itemids, titles, year, strand_info, country, countrycomments, edusetting, edusettingcomments, pub, pubcomments, design, 
                           designcomment, outcometext, interventiontext, studyrealism, studyrealismcomment, partassignment, partassigncomments,
                           levelofassignment, assigncomment, age, agecomments, studentgender, studentgendercomments, SMD, SESMD, CIupperSMD,
                           CIlowerSMD, codes_check, outcomes_check, outcomecodes_check)), 
               columns =['ItemId', 'Author', 'Year', 'Strand', 'Country', 'CountryComments', 'EducationalSetting', 'EducationalSettingComments', 'PublicationType', 'PublicationTypeComments',
                         'StudyDesign', 'StudyDesignComments','Outcome', 'Intervention', 'StudyRealism', 'StudyRealismComments', 'ParticipantAssignment', 'ParticipantAssignmentComments',
                         'LevelofAssignment', 'LevelofAssignmentComments', 'StudentAge', 'StudentAgeComments', 'StudentGender', 'StudentGenderComments', 'SMD', 'SESMD', 'CIupperSMD', 
                         'CIlowerSMD', 'Codes section present', 'Outcomes section present', 'OutcomeCodes section present']) 

df["LevelofAssignment"] = df["LevelofAssignment"].apply(", ".join)
df["ParticipantAssignment"] = df["ParticipantAssignment"].apply(", ".join)
df["EducationalSetting"] = df["EducationalSetting"].apply(", ".join)
df["Country"] = df["Country"].apply(", ".join)
df["Strand"] = df["Strand"].str.replace("Toolkit: ", "")

# add decade column
def decade_row(row):
  if row["Year"] >= 1960 and row["Year"] <= 1969:
    decade="1960-1969"
  elif row["Year"] >= 1970 and row["Year"] <= 1979:
    decade="1970-1979"
  elif row["Year"] >= 1980 and row["Year"] <= 1989:
    decade="1980-1989"
  elif row["Year"] >= 1990 and row["Year"] <= 1999:
    decade="1990-1999"
  elif row["Year"] >= 2000 and row["Year"] <= 2009:
    decade="2000-2010"
  elif row["Year"] >= 2010 and row["Year"] <= 2019:
    decade="2010-2019"
  elif row["Year"] >= 2019 and row["Year"] <= 2029:
    decade="2020-2029"
  return decade

def random_row(row):
  if row["StudyDesign"] == "Prospective QED" or row["StudyDesign"]=="Retrospective QED  " or row["StudyDesign"] == "Interrupted time series QED" or row["StudyDesign"] =="RegressionDiscontinuity - not randomised":
    outcome="Non-random"
  elif row["StudyDesign"]=="Individual RCT" or row["StudyDesign"]=="Cluster RCT" or row["StudyDesign"]=="Multisite RCT" or row["StudyDesign"]=="Regression Discontinuity - not randomised":
    outcome="Random"
  else:
    outcome="NA"
  return outcome

df["Decade"] = df.apply(decade_row, axis=1)
df["Randomisation"] = df.apply(random_row, axis=1)

# reorder columns
df = df[["ItemId", "Author", "Year", "Decade", "Strand", "Country", "CountryComments", "Outcome", "PublicationType", "PublicationTypeComments",
         "EducationalSetting", "EducationalSettingComments", "Intervention", "StudentAge", "StudentAgeComments", "StudentGender", "StudentGenderComments",
         "StudyRealism", "StudyRealismComments", "LevelofAssignment", "LevelofAssignmentComments", "StudyDesign",
         "StudyDesignComments", "ParticipantAssignment", "ParticipantAssignmentComments", "Randomisation", "SMD", "SESMD", "CIupperSMD", "CIlowerSMD",
         'Codes section present', 'Outcomes section present', 'OutcomeCodes section present']]
df["StudentAgeComments"]
```

```{r}
all <- data.frame(py$df)

all$SMD <- as.character(all$SMD)
all$SMD[all$SMD=="NA"] <- NA
all$SMD <- as.numeric(all$SMD)

all$SESMD <- as.character(all$SESMD)
all$SESMD[all$SESMD=="NA"] <- NA
all$SESMD <- as.numeric(all$SESMD)

all$CIupperSMD <- as.character(all$CIupperSMD)
all$CIupperSMD[all$CIupperSMD=="NA"] <- NA
all$CIupperSMD <- as.numeric(all$CIupperSMD)

all$StudyRealism <- as.character(all$StudyRealism)
all$StudyRealism[all$StudyRealism=="NA"] <- NA
all$StudyRealism <- as.factor(all$StudyRealism)

all$StudentAge <- as.character(all$StudentAge)
all$StudentAge[all$StudentAge=="list()"] <- NA
all$StudentAge <- as.factor(all$StudentAge)

all$StudentGenderComments <- as.character(all$StudentGenderComments)
all$StudentGenderComments[all$StudentGenderComments=="list()"] <- NA
all$StudentGenderComments[all$StudentGenderComments==""] <- NA
all$StudentGenderComments <- as.factor(all$StudentGenderComments)

all$ParticipantAssignment <- as.character(all$ParticipantAssignment)
all$ParticipantAssignment[all$ParticipantAssignment=="NA"] <- NA
all$ParticipantAssignment <- as.factor(all$ParticipantAssignment)

all$ParticipantAssignmentComments <- as.character(all$ParticipantAssignmentComments)
all$ParticipantAssignmentComments[all$ParticipantAssignmentComments=="list()"] <- NA
all$ParticipantAssignmentComments[all$ParticipantAssignmentComments==""] <- NA
all$ParticipantAssignmentComments <- as.factor(all$ParticipantAssignmentComments)

all$EducationalSettingComments <- as.character(all$EducationalSettingComments)
all$EducationalSettingComments[all$EducationalSettingComments=="list()"] <- NA
all$EducationalSettingComments[all$EducationalSettingComments==""] <- NA
all$EducationalSettingComments[all$EducationalSettingComments=='c("", "")'] <- NA
all$EducationalSettingComments[all$EducationalSettingComments=='c("", "", "")'] <- NA
all$EducationalSettingComments <- as.factor(all$EducationalSettingComments)

all$CountryComments <- as.character(all$CountryComments)
all$CountryComments[all$CountryComments=="list()"] <- NA
all$CountryComments[all$CountryComments==""] <- NA
all$CountryComments[all$CountryComments=='c("", "")'] <- NA
all$CountryComments[all$CountryComments=='c("", "", "")'] <- NA
all$CountryComments <- as.factor(all$CountryComments)

all$PublicationTypeComments <- as.character(all$PublicationTypeComments)
all$PublicationTypeComments[all$PublicationTypeComments=="list()"] <- NA
all$PublicationTypeComments[all$PublicationTypeComments==""] <- NA
all$PublicationTypeComments[all$PublicationTypeComments=='c("", "")'] <- NA
all$PublicationTypeComments <- as.factor(all$PublicationTypeComments)

all$StudentAgeComments <- as.character(all$StudentAgeComments)
all$StudentAgeComments[all$StudentAgeComments=="list()"] <- NA
all$StudentAgeComments[all$StudentAgeComments=='c("", "")'] <- NA
all$StudentAgeComments[all$StudentAgeComments=='c("", "", "")'] <- NA
all$StudentAgeComments[all$StudentAgeComments=='c("", "", "", "")'] <- NA
all$StudentAgeComments[all$StudentAgeComments=='c("", "", "", "", "")'] <- NA
all$StudentAgeComments[all$StudentAgeComments=='c("", "", "", "", "", "")'] <- NA
all$StudentAgeComments <- as.factor(all$StudentAgeComments)

all$StudyDesignComments <- as.character(all$StudyDesignComments)
all$StudyDesignComments[all$StudyDesignComments=="list()"] <- NA
all$StudyDesignComments[all$StudyDesignComments==""] <- NA
all$StudyDesignComments <- as.factor(all$StudyDesignComments)

all$StudyRealismComments <- as.character(all$StudyRealismComments)
all$StudyRealismComments[all$StudyRealismComments=="list()"] <- NA
all$StudyRealismComments[all$StudyRealismComments==""] <- NA
all$StudyRealismComments <- as.factor(all$StudyRealismComments)

all$LevelofAssignmentComments <- as.character(all$LevelofAssignmentComments)
all$LevelofAssignmentComments[all$LevelofAssignmentComments=="list()"] <- NA
all$LevelofAssignmentComments[all$LevelofAssignmentComments==""] <- NA
all$LevelofAssignmentComments <- as.factor(all$LevelofAssignmentComments)

all$LevelofAssignment <- as.character(all$LevelofAssignment)
all$LevelofAssignment[all$LevelofAssignment=="NA"] <- NA
all$LevelofAssignment <- as.factor(all$LevelofAssignment)

all$Decade <- as.character(all$Decade)
all$Decade[all$Decade==""] <- NA
all$Decade <- as.factor(all$Decade)

all$Randomisation <- as.character(all$Randomisation)
all$Randomisation[all$Randomisation==""] <- NA
all$Randomisation <- as.factor(all$Randomisation)

all$CIlowerSMD <- as.character(all$CIlowerSMD)
all$CIlowerSMD[all$CIlowerSMD=="NA"] <- NA
all$CIlowerSMD <- as.numeric(all$CIlowerSMD)

all$Intervention <- as.character(all$Intervention)
all$Intervention[all$Intervention=="NA"] <- NA
all$Intervention[all$Intervention==""] <- NA
all$Intervention <- as.factor(all$Intervention)

all$Outcome <- as.character(all$Outcome)
all$Outcome[all$Outcome=="NA"] <- NA
all$Outcome <- as.factor(all$Outcome)

all$SMD = round(all$SMD, 4)
all$SESMD = round(all$SMD, 4)
all$CIupperSMD = round(all$SMD, 4)
all$CIlowerSMD = round(all$SMD, 4)

View(all)
df_new = data.frame(lapply(all, as.character), stringsAsFactors=FALSE)

write.csv(df_new, "May12thExtraction_with_comments.csv", row.names=FALSE)
```